Articles of Association of London Hackspace Ltd

### 2014-12-10 constitution/articles-body.tex
Fix heading position (thanks Oxford!)
Clarify retirement of existing directors

\item
  \begin{enumerate}
  \item
    A resolution in writing agreed by a simple majority (or in the case
    of a special resolution by a majority of not less than 75\%) of the
    members who would have been entitled to vote upon it had it been
    proposed at a general meeting shall be effective provided that:
    \begin{enumerate}
    \item
      a copy of the proposed resolution has been sent to every eligible
      member;
    \item
      a simple majority (or in the case of a special resolution a
      majority of not less than 75\%) of members has signified its
      agreement to the resolution; and
    \item
      it is contained in an authenticated document which has been
      received at the registered office within the period of 28 days
      beginning with the circulation date.
    \end{enumerate}
  \item
    A resolution in writing may comprise several copies to which one or
    more members have signified their agreement.
  \item
    In the case of a member that is an organisation, its authorised
    representative may signify its agreement.
  \end{enumerate}
\item
  Every member, whether an individual or an organisation, shall have one vote.

@@

@@

\section{Directors Elections}
\item
  \begin{enumerate}
    \item Directors elections must be called by the Board
      \begin{enumerate}
        \item in the case of the first election: before the end of the calendar year following
                the year in which the association was created.
        \item in the case of subsequent elections: before the end of the calendar year following
                the year in which the last election was held.
      \end{enumerate}
    \item
      The directors election must be carried out by electronically polling the membership as follows:
      \begin{enumerate}
        \item The Meek STV voting method with a "no further places" candidate must be used.
        \item All members of the association at the time the election commences are eligible to vote.
        \item The voting period of the election must be no less than 14 days and no more than 28 days.
        \item The quorum of the election must be at least 10\% of eligible voters.
      \end{enumerate}
    \item Directors standing for re-election will remain directors until the successful conclusion
          of the election.
    \item Notice of the election must be given at the time the election starts to all members eligible
          to vote who have registered an electronic mail address with the association.
   \end{enumerate}

>>>>

\item
  \begin{enumerate}
  \item
    A resolution in writing agreed by a simple majority (or in the case
    of a special resolution by a majority of not less than 75\%) of the
    members who would have been entitled to vote upon it had it been
    proposed at a general meeting shall be effective provided that:
    \begin{enumerate}
    \item
      a copy of the proposed resolution has been sent to every eligible
      member;
    \item
      a simple majority (or in the case of a special resolution a
      majority of not less than 75\%) of members has signified its
      agreement to the resolution; and
    \item
      it is contained in an authenticated document which has been
      received at the registered office within the period of 28 days
      beginning with the circulation date.
    \end{enumerate}
  \item
    A resolution in writing may comprise several copies to which one or
    more members have signified their agreement.
  \item
    In the case of a member that is an organisation, its authorised
    representative may signify its agreement.
  \end{enumerate}

@@

\item
  Every member, whether an individual or an organisation, shall have one vote.

@@

\section{Directors Elections}
\item
  \begin{enumerate}
    \item Directors elections must be called by the Board
      \begin{enumerate}
        \item in the case of the first election: before the end of the calendar year following
                the year in which the association was created.
        \item in the case of subsequent elections: before the end of the calendar year following
                the year in which the last election was held.
      \end{enumerate}
    \item
      The directors election must be carried out by electronically polling the membership as follows:
      \begin{enumerate}
        \item The Meek STV voting method with a "no further places" candidate must be used.
        \item All members of the association at the time the election commences are eligible to vote.
        \item The voting period of the election must be no less than 14 days and no more than 28 days.
        \item The quorum of the election must be at least 10\% of eligible voters.
      \end{enumerate}
    \item A director standing for re-election will remain a director until the successful conclusion
          of the election.
    \item A director retiring and not standing for re-election will cease to be a director at the
          start of the election.
    \item Notice of the election must be given at the time the election starts to all members eligible
          to vote who have registered an electronic mail address with the association.
   \end{enumerate}
